### 2020-04-18 README.Rmd
Edits to Context and Methods

SARS-CoV2  
COVID-19  
Temperature  
Humidity  
Spatial SUR  
Contagion  
Spain

@@

## Introduction

@@

## Context, Data, and Methods

### Covid-19 in Spain

When was the first case reported? When did the country close international arrivals? When did initial measures of social distancing were implemented? The lockdown?

### Selection of Variables

@@

### Sources of Data

Our dataset includes information about the daily number of cases of COVID-19 reported in Spain \footnote{cases tested} at the provincial level (NUTIII in eurostat terminology) from March 13th to April 11th (30 days and 50 spatial units). The Spanish National Government publishes periodic updates at the regional level (NUTII) and the information is also released at the provincial level as part of a collaborative project. This information is compiled from several sources, mainly the official web pages of the Spanish regional goverments. In addition, we consider two sets of explanatory variables. The first one, and the focus of this research, is set of two environmental variables, namely temperature and humidity. The second set provides some relevant controls for multivariate analysis, and refers to economic and demographic attributes of the province. Table \ref{tab:descriptive-statistics} shows the descriptive statistics and the provencance of the data.

```{r descriptive-statistics, echo=FALSE}
data.frame(Variable = c("COVID-19 Incidence",
                        "GDPpc", 
                        "Older", 
                        "Population Density",
                        "Mean Temperature",
                        "Humidity"),
           Note = c("Incidence in reported cases of SARS-19 per 100,000 people",
                    "GDP per capita in €1,000s",
                    "Percentage of people aged 65 and older in the province",
                    "Population density in the province in people per sq.km",
                    "Mean temperature in province by date, in C",
                    "Relative humidity in province by date"),
           Min = c(min(covid19_spain$Incidence),
                   min(provinces_spain$GDPpc),
                   min(provinces_spain$Older),
                   min(provinces_spain$Density),
                   min(covid19_spain$Mean_Temp),
                   min(covid19_spain$Humidity)),
           Mean = c(mean(covid19_spain$Incidence),
                   mean(provinces_spain$GDPpc),
                   mean(provinces_spain$Older),
                   mean(provinces_spain$Density),
                   mean(covid19_spain$Mean_Temp),
                   mean(covid19_spain$Humidity)),
           Max = c(max(covid19_spain$Incidence),
                   max(provinces_spain$GDPpc),
                   max(provinces_spain$Older),
                   max(provinces_spain$Density),
                   max(covid19_spain$Mean_Temp),
                   max(covid19_spain$Humidity)),
           SD = c(sd(covid19_spain$Incidence),
                   sd(provinces_spain$GDPpc),
                   sd(provinces_spain$Older),
                   sd(provinces_spain$Density),
                   sd(covid19_spain$Mean_Temp),
                   sd(covid19_spain$Humidity)),
           Source = c("Montera34",
                      "INE",
                      "INE",
                      "INE",
                      "AEMET",
                      "MAPA")) %>%
  kable("html",
        booktabs = TRUE,
        digits = 2,
        caption = "\\label{tab:descriptive-statistics}Descriptive statistics") %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  footnote(general = c("Montera34: https://code.montera34.com:4443/numeroteca/covid19/-/blob/master/README_providencialdata19.md", 
                       "INE (Instituto Nacional de Estadistica): https://www.ine.es/",
                       "AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es",
                       "MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es"))
```

### Methods: Spatial SUR

Seemingly Unrelated Regressions are used in the context of...

@@

\begin{equation}
\label{eq:sur-sim}
\begin{bmatrix}
y_1 \\ y_2 \\ \vdots \\ y_T
\end{bmatrix}
=
\begin{bmatrix}
X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T
\end{bmatrix}
\
\begin{bmatrix}
\beta_1 \\ \beta_1 \\ \vdots \\ \beta_T
\end{bmatrix}
+
\begin{bmatrix}
\epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T
\end{bmatrix}
\end{equation}

\noindent where $y_{t}=(y_{1t},...,y_{Nt})$ is a $N \times 1$ vector, and in our case $y_{st}$ is the incidence ratio in the province $s$ ($s=1,...,N$) the day $t$ $(t=1,...,T)$; $X_t=(X^1,...,X^{k_t})$ is a $N \times k_t$ matrix of the $k_t$ independent variables, $X_i=(X^i_{st})$; $\beta_t=(\beta_{1t},...,\beta_{Nt})$ is a vector of coefficients and $\epsilon_t=(\epsilon_{1t},...,\epsilon_{Nt})$ is the vector of residuals.

@@

\begin{equation}
\label{eq:sur-err}
E[\epsilon_t \epsilon'_{t'}]=\sigma_{tt'}
\end{equation}

Note that this specification is very flexible, in that it allows changes in the coefficients $\beta_{it}$ in order to modulate the effect of $X^i_{.t}$ on $y_t$. This flexibility can be reduced and it is posible to impose restrinctions considering some $\beta$ coefficients as being constant over time. In this case, we can reformulate the coefficients expression of $\beta_t = (\beta_{1}, \cdots, \beta_{r-1}, \beta_{r}, \beta_{r+1}, \cdots, \beta_{Nt})$ considering the first $r$ coefficients contanst.

@@

\begin{equation}
y = X \beta + \epsilon
\end{equation}

@@

\begin{equation}
\label{eq:sur-slm}
\bf{A}y = X \beta + \epsilon \\
\epsilon =N(0,\Omega)
\end{equation}

\noindent where A =$I_{TN}-\bf{\Lambda} \otimes W$ with $\bf{\Lambda} = diag(\lambda_1, \cdots, \lambda_T)$.

This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Parameters of spatial dependence are estimated for each time period $\lambda_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\lambda_i=\lambda_j, \forall i,j$). The correspond Wald test is available in the R package **spsur**

@@

### SUR Models

@@

Summary of best model.
```{r summary-best-model, echo=FALSE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
                   pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)"), 29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable("html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```

## Discussion

@@

## Concluding Remarks

@@

## Acknowledgments

The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

## References

>>>>

SARS-CoV2  
COVID-19  
Seasonality  
Temperature  
Humidity  
Spatial SUR  
Contagion  
Spain

@@

Introduction
==========================

@@

Context, Data, and Methods
============

## Covid-19 in Spain

For a better interpretation of the results of our analysis is necessary to know the chronology of the epidemic outbreak in Spain. This subsection presents a brief time line of COVID-19.

The first reported case of COVID-19 in Spain was on January 31th, were a German tourist in the Canary Islands was positively tested, but the first not imported case was diagnostic on February 27th in Sevilla province (Andalusia). The epidemic was growing slowly at the beginning but in March 11th the World Health Organization (WHO) declared officially the pandemic. This declaration was a break point and on March 13th the Spanish National Government declare the "Emergency Status". At this date, Spain have been declared 4209 cases of COVID-19 (mostly of cases, 1990, in Madrid). Only essential services (e.g. food, health) and some economic subsector of industry and construction could to maintain activity. On March 17th Spain closes its lands borders and only allows entry to nationals and residents. From March 30th to April 12th (April 10th-12th Easter) lockdown of the Spanish people was hardened and only essential activities were allowed.

## Selection of Variables

@@

## Sources of Data

Our dataset includes information about the daily number of cases of COVID-19 reported in Spain at the provincial level (NUTIII in Eurostat terminology) for the period between March 13th and April 11th, inclusive. This gives a temporal coverage of 30 days and spatial coverage of 50 units. For our purposes, we consider positive cases reported, but excluding symptomatic cases diagnosed by a doctor without a Polymerase Chain Reaction (PCR) test. The Spanish National Government publishes periodic updates at the regional level (NUTII) and the information is also released at the provincial level as part of a collaborative project [**by whom?**]. This information is compiled from several sources, mainly the official web pages of the Spanish regional goverments. In addition, we consider two sets of explanatory variables. The first one, and the focus of this research, is set of two environmental variables, namely temperature and humidity, which are collected from official sources (i.g., AEMET, the state meteorology agency, and MAPA, the ministry of agriculture, fisheries, and food). The second set provides some relevant controls for multivariate analysis, and refers to economic and demographic attributes of the province (also collected from official sources, i.e., INE, the national statistics institute). Table \ref{tab:descriptive-statistics} shows the descriptive statistics and the provenance of the data.

```{r descriptive-statistics, echo=FALSE}
data.frame(Variable = c("COVID-19 Incidence",
                        "GDPpc", 
                        "Older", 
                        "Population Density",
                        "Mean Temperature",
                        "Humidity"),
           Note = c("Incidence in reported cases of SARS-19 per 100,000 people",
                    "GDP per capita in €1,000s",
                    "Percentage of people aged 65 and older in the province",
                    "Population density in the province in people per sq.km",
                    "Mean temperature in province by date, in C",
                    "Relative humidity in province by date"),
           Min = c(min(covid19_spain$Incidence),
                   min(provinces_spain$GDPpc),
                   min(provinces_spain$Older),
                   min(provinces_spain$Density),
                   min(covid19_spain$Mean_Temp),
                   min(covid19_spain$Humidity)),
           Mean = c(mean(covid19_spain$Incidence),
                   mean(provinces_spain$GDPpc),
                   mean(provinces_spain$Older),
                   mean(provinces_spain$Density),
                   mean(covid19_spain$Mean_Temp),
                   mean(covid19_spain$Humidity)),
           Max = c(max(covid19_spain$Incidence),
                   max(provinces_spain$GDPpc),
                   max(provinces_spain$Older),
                   max(provinces_spain$Density),
                   max(covid19_spain$Mean_Temp),
                   max(covid19_spain$Humidity)),
           SD = c(sd(covid19_spain$Incidence),
                   sd(provinces_spain$GDPpc),
                   sd(provinces_spain$Older),
                   sd(provinces_spain$Density),
                   sd(covid19_spain$Mean_Temp),
                   sd(covid19_spain$Humidity)),
           Source = c("Montera34",
                      "INE",
                      "INE",
                      "INE",
                      "AEMET",
                      "MAPA")) %>%
  kable(#"latex",
        "html",
        booktabs = TRUE,
        digits = 2,
        caption = "\\label{tab:descriptive-statistics}Descriptive statistics") %>%
  #kable_styling(latex_options = c("striped", "scale_down")) %>%
#kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(7, width = "5em") %>%
  footnote(general = c("Montera34: https://code.montera34.com:4443/numeroteca/covid19/-/blob/master/README_providencialdata19.md", 
                       "INE (Instituto Nacional de Estadistica): https://www.ine.es/",
                       "AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es",
                       "MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es"))
```

## Methods: Spatial SUR

The Seemingly Unrelated Regression equations model (SUR from now on) is a multivariate econometric formulation used in different fields when the data set is organized as cross-sections for different time periods. The basis of this approach is well-known since the initial works of Zellner [-@Zellner1962efficient] and now is a popular methodology included in several Econometrics textbook [e.g., @Greene2003econometric]. To our knowledge, @Anselin1988spatial was the first text that introduced the term spatial SUR in reference to a model made of ‘an equation for each time period, which is estimated for a cross section of spatial units’ (p. 141). From this milestone, a huge researches used this methodology in spatial framework. Rey and Montouri [-@Rey1999us], Fingleton [-@Fingleton2007multi], Lauridsen et al. [-@Lauridsen2010spatiotemporal], Le Gallo and Dall’Erba [-@Legallo2006evaluating], and Lopez et al. [-@Lopez2017spatial] are well-known examples in this line.

@@

<!--
\begin{equation}
\label{eq:sur-sim}
\begin{bmatrix}
y_1 \\ y_2 \\ \vdots \\ y_T
\end{bmatrix}
=
\begin{bmatrix}
X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T
\end{bmatrix}
\
\begin{bmatrix}
\beta_1 \\ \beta_1 \\ \vdots \\ \beta_T
\end{bmatrix}
+
\begin{bmatrix}
\epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T
\end{bmatrix}
\end{equation}

\noindent where $y_{t}=(y_{1t},...,y_{Nt})$ is an $N \times 1$ vector, and in our case $y_{st}$ is the incidence ratio in the province $s$ ($s=1,...,N$) the day $t$ $(t=1,...,T)$; $X_t=(X^1,...,X^{k_t})$ is a $N \times k_t$ matrix of the $k_t$ independent variables, $X_i=(X^i_{st})$; $\beta_t=(\beta_{1t},...,\beta_{Nt})$ is a vector of coefficients and $\epsilon_t=(\epsilon_{1t},...,\epsilon_{Nt})$ is the vector of residuals.
-->

<!--Equations for README.md generated using this app https://alexanderrodin.com/github-latex-markdown/-->
![\begin{equation} \label{eq:sur-sim} \begin{bmatrix} y_1 \\ y_2 \\ \vdots \\ y_T \end{bmatrix} = \begin{bmatrix} X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T \end{bmatrix} \ \begin{bmatrix} \beta_1 \\ \beta_1 \\ \vdots \\ \beta_T \end{bmatrix} + \begin{bmatrix} \epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T \end{bmatrix} \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-sim%7D%20%5Cbegin%7Bbmatrix%7D%20y_1%20%5C%5C%20y_2%20%5C%5C%20%5Cvdots%20%5C%5C%20y_T%20%5Cend%7Bbmatrix%7D%20%3D%20%5Cbegin%7Bbmatrix%7D%20X_1%20%26%200%20%26%20%5Ccdots%20%26%200%20%5C%5C%200%20%26%20X_2%20%26%20%5Ccdots%20%26%200%20%5C%5C%20%5Cvdots%20%26%20%5Cvdots%20%26%20%5Cddots%20%26%20%5Cvdots%20%5C%5C%200%20%26%200%20%26%20%5Ccdots%20%26%20X_T%20%5Cend%7Bbmatrix%7D%20%5C%20%5Cbegin%7Bbmatrix%7D%20%5Cbeta_1%20%5C%5C%20%5Cbeta_1%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cbeta_T%20%5Cend%7Bbmatrix%7D%20%2B%20%5Cbegin%7Bbmatrix%7D%20%5Cepsilon_1%20%5C%5C%20%5Cepsilon_2%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cepsilon_T%20%5Cend%7Bbmatrix%7D%20%5Cend%7Bequation%7D)

\noindent where ![$y_{t}=(y_{1t},...,y_{Nt})$](https://render.githubusercontent.com/render/math?math=%24y_%7Bt%7D%3D(y_%7B1t%7D%2C...%2Cy_%7BNt%7D)%24) is an ![$N \times 1$](https://render.githubusercontent.com/render/math?math=%24N%20%5Ctimes%201%24) vector, and in our case ![$y_{st}$](https://render.githubusercontent.com/render/math?math=%24y_%7Bst%7D%24) is the incidence ratio in the province ![$s\text{ }(s=1,...,N)$](https://render.githubusercontent.com/render/math?math=%24s%5Ctext%7B%20%7D(s%3D1%2C...%2CN)%24) the day ![$t\text{ }(t=1,...,T)$](https://render.githubusercontent.com/render/math?math=%24t%5Ctext%7B%20%7D(t%3D1%2C...%2CT)%24); ![$X_t=(X^1,...,X^{k_t})$](https://render.githubusercontent.com/render/math?math=%24X_t%3D(X%5E1%2C...%2CX%5E%7Bk_t%7D)%24) is a ![$N \times k_t$](https://render.githubusercontent.com/render/math?math=%24N%20%5Ctimes%20k_t%24) matrix of the ![$k_t$](https://render.githubusercontent.com/render/math?math=%24k_t%24) independent variables, ![$X_i=(X^i_{st})$](https://render.githubusercontent.com/render/math?math=%24X_i%3D(X%5Ei_%7Bst%7D)%24); ![$\beta_t=(\beta_{1t},...,\beta_{Nt})$](https://render.githubusercontent.com/render/math?math=%24%5Cbeta_t%3D(%5Cbeta_%7B1t%7D%2C...%2C%5Cbeta_%7BNt%7D)%24) is a vector of coefficients and ![$\epsilon_t=(\epsilon_{1t},...,\epsilon_{Nt})$](https://render.githubusercontent.com/render/math?math=%24%5Cepsilon_t%3D(%5Cepsilon_%7B1t%7D%2C...%2C%5Cepsilon_%7BNt%7D)%24) is the vector of residuals.

@@

<!--
\begin{equation}
\label{eq:sur-err}
E[\epsilon_t \epsilon'_{t'}]=\sigma_{tt'}
\end{equation}

Note that this specification is very flexible, in that it allows changes in the coefficients $\beta_{it}$ in order to modulate the effect of $X^i_{.t}$ on $y_t$. This flexibility can be reduced and it is posible to impose restrinctions considering some $\beta$ coefficients as being constant over time. In this case, we can reformulate the coefficients expression of $\beta_t = (\beta_{1}, \cdots, \beta_{r-1}, \beta_{r}, \beta_{r+1}, \cdots, \beta_{Nt})$ to restrict the first $r$ coefficients to be constant across equations, i.e., time periods.
-->

![\begin{equation} \label{eq:sur-err} E\[\epsilon_t \epsilon'_{t'}\]=\sigma_{tt'} \end{equation} ](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-err%7D%20E%5B%5Cepsilon_t%20%5Cepsilon'_%7Bt'%7D%5D%3D%5Csigma_%7Btt'%7D%20%5Cend%7Bequation%7D%20)

Note that this specification is very flexible, in that it allows changes in the coefficients ![$\beta_{it}$](https://render.githubusercontent.com/render/math?math=%24%5Cbeta_%7Bit%7D%24) in order to modulate the effect of ![$X^i_{.t}$](https://render.githubusercontent.com/render/math?math=%24X%5Ei_%7B.t%7D%24) on ![$y_t$](https://render.githubusercontent.com/render/math?math=%24y_t%24). This flexibility can be reduced and it is posible to impose restrinctions considering some ![$\beta$](https://render.githubusercontent.com/render/math?math=%24%5Cbeta%24) coefficients as being constant over time. In this case, we can reformulate the coefficients expression of ![$\beta_t = (\beta_{1}, \cdots, \beta_{r-1}, \beta_{r}, \beta_{r+1}, \cdots, \beta_{Nt})$](https://render.githubusercontent.com/render/math?math=%24%5Cbeta_t%20%3D%20(%5Cbeta_%7B1%7D%2C%20%5Ccdots%2C%20%5Cbeta_%7Br-1%7D%2C%20%5Cbeta_%7Br%7D%2C%20%5Cbeta_%7Br%2B1%7D%2C%20%5Ccdots%2C%20%5Cbeta_%7BNt%7D)%24) to restrict the first ![$r$](https://render.githubusercontent.com/render/math?math=%24r%24) coefficients to be constant across equations, i.e., time periods.

@@

<!--
\begin{equation}
y = X \beta + \epsilon
\end{equation}
-->

![\begin{equation} y = X \beta + \epsilon \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20y%20%3D%20X%20%5Cbeta%20%2B%20%5Cepsilon%20%5Cend%7Bequation%7D)

@@

<!--
\begin{equation}
\label{eq:sur-slm}
\bf{A}y = X \beta + \epsilon \\
\epsilon =N(0,\Omega)
\end{equation}

\noindent where $A =I_{TN}-\bf{\rho} \otimes W$ with $\bf{\rho} = diag(\rho_1, \cdots, \rho_T)$.
-->

![\begin{equation} \label{eq:sur-slm} \bf{A}y = X \beta + \epsilon \\ \epsilon =N(0,\Omega) \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-slm%7D%20%5Cbf%7BA%7Dy%20%3D%20X%20%5Cbeta%20%2B%20%5Cepsilon%20%5C%5C%20%5Cepsilon%20%3DN(0%2C%5COmega)%20%5Cend%7Bequation%7D)

\noindent where ![$A =I_{TN}-\bf{\rho} \otimes W$ with $\bf{\rho} = diag(\rho_1, \cdots, \rho_T)$](https://render.githubusercontent.com/render/math?math=%24A%20%3DI_%7BTN%7D-%5Cbf%7B%5Crho%7D%20%5Cotimes%20W%24%20with%20%24%5Cbf%7B%5Crho%7D%20%3D%20diag(%5Crho_1%2C%20%5Ccdots%2C%20%5Crho_T)%24).

<!--
This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period $\rho_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\rho_i=\rho_j, \forall i,j$). The correspond Wald test is available in the R package `spsur`. 
-->

This specification assumes that incidence in a province (![$y_st$](https://render.githubusercontent.com/render/math?math=%24y_st%24)) at time ![$t$](https://render.githubusercontent.com/render/math?math=%24t%24) is partially determined by the weighted average ![($Wy_{st}$)](https://render.githubusercontent.com/render/math?math=(%24Wy_%7Bst%7D%24)) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period ![$\rho_t$](https://render.githubusercontent.com/render/math?math=%24%5Crho_t%24) and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence (![$\rho_i=\rho_j, \forall i,j$](https://render.githubusercontent.com/render/math?math=%24%5Crho_i%3D%5Crho_j%2C%20%5Cforall%20i%2Cj%24)). The correspond Wald test is available in the R package `spsur`.

@@

## SUR Models

@@

Summary of best model.
```{r summary-best-model, echo=FALSE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
                   pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)"), 29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable(#"latex",
        "html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  #kable_styling(latex_options = c("striped", "scale_down")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```

Discussion
===================

@@

Concluding Remarks
===================

@@

Acknowledgments {#acknowledgments .unnumbered}
==========

Add acknowledgments as appropriate in final draft.

The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `aemet` [], `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

References {#references .unnumbered}
==========
